How cryptic is cryptic diversity? Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-05-03 documents/turtle_report.tex
support for ROC based model selection added.

\documentclass{article}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

@@

@@

% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Mon Apr  8 09:29:56 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rr}
  \hline
 & tmorph.dac \\ 
  \hline
1 & 722 \\ 
  2 &   1 \\ 
  3 &   1 \\ 
  4 &   1 \\ 
  5 &   1 \\ 
   \hline
\end{tabular}
\caption{Number of specimens assigned to optimal number of partitions as determined by dissimilarity based EAC. Each column corresponds to a different partition, with the number assigned directly below it.}
\label{tab:dac}
\end{center}
\end{table}

@@

@@

% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Mon Apr  8 09:29:56 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrr}
  \hline
 & CCR & marm & pall \\ 
  \hline
CCR &  40 &  14 &  11 \\ 
  marm &  25 &  74 &   2 \\ 
  pall &   3 &   1 &  10 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for sh1 classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-sh1}
\end{center}
\end{table}
% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Mon Apr  8 09:29:56 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrr}
  \hline
 & CCR & marm & pall \\ 
  \hline
CCR &  44 &  12 &  10 \\ 
  marm &  17 &  82 &   6 \\ 
  pall &   2 &   1 &   7 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for sh2 classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-sh2}
\end{center}
\end{table}
% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Mon Apr  8 09:29:56 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & CCR & marm & pall & SJ \\ 
  \hline
CCR &  37 &  11 &   9 &   2 \\ 
  marm &  18 &  59 &   3 &  10 \\ 
  pall &   7 &   2 &  10 &   0 \\ 
  SJ &   1 &   4 &   1 &   7 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for sh3 classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-sh3}
\end{center}
\end{table}
% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Mon Apr  8 09:29:56 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & 1 & 2 & 3 & 4 \\ 
  \hline
1 & 107 &   9 &  13 &  13 \\ 
  2 &   1 &   8 &   0 &   0 \\ 
  3 &   4 &   0 &   8 &   3 \\ 
  4 &   4 &   0 &   2 &   8 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for spinks classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-spinks}
\end{center}
\end{table}

@@

@@

@@

@@

>>>>

% this document has the propensity to become outdated as the code base
% and results are updated over time. the pdf file should represent the most
% stable implementation of this document.
%
% this is the basic ``template'' for all reports for meetings with ken and to
% send to collaborators.
\documentclass{article}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/gap}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/a-gap}

\end{knitrout}

@@

% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Fri May  3 10:50:12 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rr}
  \hline
 & tmorph.dac \\ 
  \hline
1 & 722 \\ 
  2 &   1 \\ 
  3 &   1 \\ 
  4 &   1 \\ 
  5 &   1 \\ 
   \hline
\end{tabular}
\caption{Number of specimens assigned to optimal number of partitions as determined by dissimilarity based EAC. Each column corresponds to a different partition, with the number assigned directly below it.}
\label{tab:dac}
\end{center}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## [1] "To speed up use option distances=FALSE"
## [1] "To speed up use option pcaoutput=FALSE"
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/gm}

\end{knitrout}

@@

% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Fri May  3 10:50:17 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrr}
  \hline
 & CCR & marm & pall \\ 
  \hline
CCR &  40 &  14 &  11 \\ 
  marm &  25 &  74 &   2 \\ 
  pall &   3 &   1 &  10 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for sh1 classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-sh1}
\end{center}
\end{table}
% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Fri May  3 10:50:17 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrr}
  \hline
 & CCR & marm & pall \\ 
  \hline
CCR &  44 &  12 &  10 \\ 
  marm &  17 &  82 &   6 \\ 
  pall &   2 &   1 &   7 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for sh2 classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-sh2}
\end{center}
\end{table}
% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Fri May  3 10:50:17 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & CCR & marm & pall & SJ \\ 
  \hline
CCR &  37 &  11 &   9 &   2 \\ 
  marm &  18 &  59 &   3 &  10 \\ 
  pall &   7 &   2 &  10 &   0 \\ 
  SJ &   1 &   4 &   1 &   7 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for sh3 classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-sh3}
\end{center}
\end{table}
% latex table generated in R 2.15.3 by xtable 1.7-0 package
% Fri May  3 10:50:17 2013
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & 1 & 2 & 3 & 4 \\ 
  \hline
1 & 107 &   9 &  13 &  13 \\ 
  2 &   1 &   8 &   0 &   0 \\ 
  3 &   4 &   0 &   8 &   3 \\ 
  4 &   4 &   0 &   2 &   8 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix for spinks classification scheme. Rows correspond to predicted class. Columns correspond to reference class. From multinomial logistic regression models.}
\label{tab:multi-conf-spinks}
\end{center}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## $sh1
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/resamp1} 
\begin{kframe}\begin{verbatim}
## 
## $sh2
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/resamp2} 
\begin{kframe}\begin{verbatim}
## 
## $sh3
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/resamp3} 
\begin{kframe}\begin{verbatim}
## 
## $spinks
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/resamp4}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## $sh1
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/multi-map1} 
\begin{kframe}\begin{verbatim}
## 
## $sh2
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/multi-map2} 
\begin{kframe}\begin{verbatim}
## 
## $sh3
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/multi-map3} 
\begin{kframe}\begin{verbatim}
## 
## $spinks
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/multi-map4}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'tnn.class' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'tnn.class.tiny' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'tnn.map' not found}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## $sh1
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/rf-map1} 
\begin{kframe}\begin{verbatim}
## 
## $sh2
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/rf-map2} 
\begin{kframe}\begin{verbatim}
## 
## $sh3
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/rf-map3} 
\begin{kframe}\begin{verbatim}
## 
## $spinks
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/rf-map4}

\end{knitrout}
